---
title: "initialdist_bargraphs"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load in packages and dataset. Then filter out irrelevant columns.
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
InitialDistibution_Table <- read_excel("C:/Purple Modeling/InitialDistibution_Table2.xlsx", 
    skip = 6)

data1 <- InitialDistibution_Table %>% select(
  InitialPublicDistribution, `avg(logodds)`, `var(logodds)`
)
```
First, I need to separate the dataset into the different initial distributions. Now, I will calculate Expectation of Accuracy, Expectation of Polarization, Predictability of Polarization, and Predictability of Accuracy.
```{r}
Idistribution<- filter(data1, InitialPublicDistribution=="IID")

distribution1<- filter(data1, InitialPublicDistribution=="1")

halfdistribution<- filter(data1, InitialPublicDistribution=="0.5")

splitdistribution<- filter(data1, InitialPublicDistribution=="split")

#split distribution calculations
aasplit<- mean(splitdistribution$`avg(logodds)`)
avsplit<- mean(splitdistribution$`var(logodds)`)
vasplit<- var(splitdistribution$`avg(logodds)`)
vvsplit<- var(splitdistribution$`var(logodds)`)

#half distribution calculations
aahalf<- mean(halfdistribution$`avg(logodds)`)
avhalf<- mean(halfdistribution$`var(logodds)`)
vahalf<- var(halfdistribution$`avg(logodds)`)
vvhalf<- var(halfdistribution$`var(logodds)`)

#IID distribution calculations
aaiid<- mean(Idistribution$`avg(logodds)`)
aviid<- mean(Idistribution$`var(logodds)`)
vaiid<- var(Idistribution$`avg(logodds)`)
vviid<- var(Idistribution$`var(logodds)`)

#1 Distribution calculations
aa1<- mean(distribution1$`avg(logodds)`)
av1<- mean(distribution1$`var(logodds)`)
va1<- var(distribution1$`avg(logodds)`)
vv1<- var(distribution1$`var(logodds)`)
```
Now I can create the final data table that I will use for the bar graphs.
```{r}
names1 = c("IID", "1", "0.5", "Split")
finaldata<- data.frame(names1)
finaldata$aa<- c(aaiid, aa1, aahalf, aasplit)
finaldata$av<- c(aviid, av1, avhalf, avsplit)
finaldata$va<- c(vaiid, va1, vahalf, vasplit)
finaldata$vv<- c(vviid, vv1, vvhalf, vvsplit)
```
Now the bar graphs!
```{r}
plot1 <- barplot(height = finaldata$aa,
                 names=finaldata$names1,
                 col=rgb(0.2,0.4,0.6,0.6),
                 main="Expectation of Accuracy Comparison", ylim=c(0,1))

plot2 <- barplot(height = finaldata$av,
                 names=finaldata$names1,
                 col=rgb(0.2,0.4,0.6,0.6),
                 main="Expectation of Polarization Comparison", ylim=c(0, .15))

plot3 <- barplot(height = finaldata$va,
                 names=finaldata$names1,
                 col=rgb(0.2,0.4,0.6,0.6),
                 main="Predictability of Accuracy Comparison", ylim=c(0, 0.08))

plot4 <- barplot(height = finaldata$vv,
                 names=finaldata$names1,
                 col=rgb(0.2,0.4,0.6,0.6),
                 main="Predictability of Polarization Comparison", ylim=c(0, 0.003))
```

